### 2014-04-16 doc/uist14/iteration3.tex
grammar iter3

\subsection{Evaluation}
We evaluate the head motion refinement method by holding an informal study and collecting qualitative feedback from a subset of 4 users from the Iteration 2 study. In the study, we asked users to try cycling through the targets using the new quasi-mode.
The users had strong preferences for the new method of refinement. On a scale from 1-7, 1 being the least mental effort and 7 being the most mental effort users rated the old technique 4.25 and the new technique 2 on average. 100\% indicated a preference for head movement to list navigation. One user referenced the issue of naming targets that the list necessitates, preferring the experience of ``matching visual cues rather than numbers''. Another participant remarked that it ``just made more sense'' and was a ``more natural way for demonstrating intentionality.'' The users prefered the new mapping in relation to the whole environment: ``it leveraged the spatial sense that I already had just by using the system''. They were also delighted to avoid list navigation, which they now called ``difficult'' and ``painful''.

>>>>

\subsection{Evaluation}
We evaluate the head motion refinement method by holding an informal study and collecting qualitative feedback from a subset of 4 users from the Iteration 2 study. In the study, we asked users to try cycling through the targets using the new quasi-mode.

The users had strong preferences for the new method of refinement. On a scale from 1-7, 1 being the least mental effort and 7 being the most mental effort users rated the old technique 4.25 and the new technique 2 on average. 100\% indicated a preference for head movement to list navigation. One user referenced the issue of naming targets that the list necessitates, preferring the experience of {\em ``matching visual cues rather than numbers’’}. Another participant remarked that it {\em ``just made more sense’’} and was a {\em``more natural way for demonstrating intentionality.’’} The users preferred the new mapping in relation to the whole environment: {\em ``it leveraged the spatial sense that I already had just by using the system’’}. They were also delighted to avoid list navigation, which they now called {\em ``difficult’’} and {\em ``painful’’}.
